### 2022-07-22 paper/paper.tex
11 test
M(r(t)) better

\section{Reference Tracking control}
00
After the reference trajectory is set, the last step is to design a controller for a agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor. Besides, its integration $\int_{0}^{t} x(\tau) d\tau$ and differentiation $\dot{x}(t)$ can also be measured by sensor respectively for PID control. Then, the output equation can be formulated as:
\begin{equation} \label{eq:agent output}
    y(t) = C\pmb{x}(t)
\end{equation}
where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is a known output matrix, and $\pmb{x}(t)=\begin{bmatrix}
    \int_{0}^{t} x^T(\tau) d\tau & x^T(t) & \dot{x}^T(t)
\end{bmatrix}^T$. Futhermore, to make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists
    \begin{enumerate*}
        \item coupling effect due to co-channel interference in communication between agents and
        \item cyber-attack on communication network between agents and ground station.
    \end{enumerate*}
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Suppose the above disturbances can be equivalently expressed as the disturbances $d_i(t), i=1,2$ in the nominal model (\ref{eq:agent}) and (\ref{eq:agent output}), the real agent model is given as:
\begin{equation} \label{eq:nonlinear sys} 
    \begin{split}
        & M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t) = u(t)\\
        & y(t) = C\pmb{x}(t) + d_2(t)
    \end{split}
\end{equation}
For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed. Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.

>>>>

\section{Reference Tracking control}
After the reference trajectory $r(t)$ is set, the last step is to design a controller for a agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. In order to transform the tracking control problem into a stability problem, we define the tracking error $e(t)\triangleq x(t)-r(t)$.
Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor. Besides, its integration $\int_{0}^{t} x(\tau) d\tau$ and differentiation $\dot{x}(t)$ can also be measured by sensor respectively for PID control. Then, the output equation can be formulated as:
\begin{equation} \label{eq:agent output}
    y(t) = C\pmb{x}(t)
\end{equation}
where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is a known output matrix, and $\pmb{x}(t)=\begin{bmatrix}
    \int_{0}^{t} x^T(\tau) d\tau & x^T(t) & \dot{x}^T(t)
\end{bmatrix}^T$. Futhermore, to make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists
    \begin{enumerate*}
        \item coupling effect due to co-channel interference in communication between agents and
        \item cyber-attack on communication network between agents and ground station.
    \end{enumerate*}
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Suppose the above disturbances can be equivalently expressed as the disturbances $d_i(t), i=1,2$ in the nominal model (\ref{eq:agent}) and (\ref{eq:agent output}), the real agent model is given as:
\begin{equation} \label{eq:nonlinear sys} 
    \begin{split}
        & M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t) = u(t)\\
        & y(t) = C\pmb{x}(t) + d_2(t)
    \end{split}
\end{equation}
For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed. Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.
